formula1

### 2019-12-15 inst/formula1.Rmd
more work

@@

```{r,equalstrength}
L1 <- loglik(indep(equalp(L2017)),L2017)
L2 <- loglik(indep(maxp(L2017)),L2017)
pchisq(2*(L2-L1),df=1,lower.tail=FALSE)
```

>>>>

In the graph above, we see that both systems consider Hamilton to be
the best.  However, F1 points place Vettel second and Bottas third,
while `hyper2` places Bottas second and Vettel third.  Overall, there
is a high degree of correlation between the two, but differences in
detail.

@@

```{r,equalstrength}
L1 <- loglik(indep(equalp(L2017)),L2017)
L2 <- loglik(indep(maxp(L2017)),L2017)
pchisq(2*(L2-L1),df=25-1,lower.tail=FALSE)
```
